Unfolding the City: \wq{Exploring Urban Spatial Attractiveness with Social Characteristics}

### 2019-04-22 template.tex

\section{Visual design}

\textcolor{blue}{Adding a background. Expert discussion. Summarize the tasks below.}

The design of the system is driven by tasks, to align the analysis of mobility patterns with individual characteristics. Before diving into the design of the system, we introduce the couple of specifical tasks the system intended for.

@@

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\linewidth]{pictures/teaser.eps}
 \caption{System Interface: (a) an interactive infographics provides the basic statistic facets of individuals; (b) a t-SNE visualization gives an overview of individuals, where the similarity in high dimensional space is preserved in 2D space; (c) data-driven profiles support users with organic individual perception; (d) group of interested individuals can be saved; (e) movement of the chosen group is visualized and explored in 2.5D main view; (f) a dock is provided to restore and compare findings; (g) different choices of 2.5D encoding can be selected.}
 \label{fig:teaser}
\end{figure}

With those design considerations, we develop a visual analytics system as Figure~\ref{fig:teaser} shows. It composes of individual panel (the left part) for individuals (\textit{Task 1}) and spatial panel (the right part) for the mobility pattern (\textit{Task 2 and 3}). In the individual panel, interactive infographics, t-SNE visualization, and data-driven profiles support users to narrow the scope down to groups of individuals with interested characteristics. With the chosen group of individuals, its moving related information is visualized and explored in a 2.5D spatio-temporal view.

@@

\subsection{t-SNE Projection of Individuals}
\textcolor{blue}{Not tsne. A octagon radar graph to position all citizens. A clustering algorithm for commend similar persons into a new group.(maybe: interactions to set the weight of each characteristic)}

>>>>

\section{Overview}
\wqc{Adding a background. Expert discussion. Summarize the tasks below.-0419}
\lmc{Add a paragraph to introduce the motivation of this work, where we derive the tasks via the interview with domain exports.-0420}

\subsection{Goal}

\wqc{Common human mobility indicators: travel distance, travel time, travel frequency, radius of gyration and movement entropy. }\\
\wq{Spatial attractiveness is an important concept in GIS. Explain why. To derive the details, we interview the expert in GIS. Some questions like, how citizens live in the city, where they live, work and entertain? Which place is popular? For different citizens, whether a place has the same attraction? ... With these questions, we summarize them into the tasks below, which need to be answered by our system.} \lm{Below are some core research concerns derived from domain exports.}

\textbf{Spatial Attractiveness} \lmc{Can we find some reference about Spatial Attractiveness. If not, we can give an explaination by ourselves.}

\textbf{Attractiveness Diversity} \lmc{Same...}

\textbf{Attractiveness Differences} \lmc{Same...}

\subsection{Tasks}

\lm{The exploration of core concepts above are resolved further with following tasks... to align the analysis of mobility patterns with individual characteristics. Before diving into the design of the system, introduce the couple of specifical tasks the system intended for.}

@@

\iffalse
\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\linewidth]{pictures/teaser.eps}
 \caption{System Interface: (a) an interactive infographics provides the basic statistic facets of individuals; (b) a t-SNE visualization gives an overview of individuals, where the similarity in high dimensional space is preserved in 2D space; (c) data-driven profiles support users with organic individual perception; (d) group of interested individuals can be saved; (e) movement of the chosen group is visualized and explored in 2.5D main view; (f) a dock is provided to restore and compare findings; (g) different choices of 2.5D encoding can be selected.}
 \label{fig:teaser}
\end{figure}
\fi

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\linewidth]{pictures/interfaceDraft.eps}
 \caption{\wq{System Interface: (a) an interactive infographics provides the basic statistic facets of individuals; (b) View1: a XXXX visualization gives an overview of individuals, where the similarity in high dimensional space is preserved in 2D space; (c) View2: data-driven profiles support users with organic individual perception; (d) View3: map view for movement of the chosen group; (e) View4: for ranking or comparison; (g) View5: top N kinds of citizens with social characteristics.}}
 \label{fig:interfaceDraft}
\end{figure}

\section{Visual Design}
\lm{With the design consideration (introduced in Section~\ref{}), we design a visual analytic system...} \lm{Show a overview figure, to introduce the relationship between multiple views}

With those design considerations, we develop a visual analytics system as \wq{Figure~\ref{fig:interfaceDraft} shows.} \wqc{instead of fig. teaser} It composes of individual panel (the left part) for individuals (\textit{Task 1}) and spatial panel (the right part) for the mobility pattern (\textit{Task 2 and 3}). In the individual panel, interactive infographics, t-SNE visualization, and data-driven profiles support users to narrow the scope down to groups of individuals with interested characteristics. With the chosen group of individuals, its moving related information is visualized and explored in a 2.5D spatio-temporal view.

@@

\wq{\subsection{XXXX Projection of Individuals}}
\wqc{A octagon radar graph to position all citizens. A clustering algorithm for commend similar persons into a new group.(maybe: interactions to set the weight of each characteristic)} \lmc{Yes, I think an interactive weight adjustment is good.}
